\section{Results}
The results given in this section aim to demonstrate how the proposed method can be used to find a scalable solution to the bus charge problem. Because the proposed solution contains various sub-problems, optimization parameters for each sub-problem may be tuned to best meet the demands of a given scenario, allowing for a wide degree of flexability that is not present in prior works which formulate solutions to the bus charge problem as a single program.
\subsection{Overall Performance}
In this section, we compare the proposed method with a baseline algorithm and a method developed by \cite{he_battery_2022} The baseline method models how bus drivers charge their electric vehicles at the Utah Transit Authority in Salt Lake City, Utah. At UTA, when bus drivers arrive at the station, they refuel their electric buses whenever a charger is available so that the number of charge sessions is maximized. The method from \cite{he_battery_2022} works somewhat differently by minimising the cost of energy with respect to the time of use tarrifs $\mu_{e-on}$ and $\mu_{e-off}$.
\par The comparison we observe is given for a 10-bus, 10-charger scenario and a single group. Each method was used to compute a charage schedule and the costs from demand, facilities, and energy charges are given in Fig. \ref{fig:results:costComparison}. Note how the baseline algorithm suffers significantly from the demand charges associated with On-Peak Power, and \cite{he_battery_2022} incurres additional cost from the facilities charges, indicating that an emphasis on energy charges and habitual charging patterns can be improved.
\par We observe where the differences in cost originate in Fig. \ref{fig:results:totalPower}. Observe how the baseline charge profile achieved the largest 15-minute average power between 19:12 adn 21:36 which is during on-peak hours and consequently yielded the large On-Peak Power charges given in Fig. \ref{fig:results:costComparison}. Additionally, note how the proposed method maintains a relatively flat power profile so that the load is balanced throughout the day which we investigate in Fig. \ref{fig:results:powerPlot}.
\par In Fig. \ref{fig:results:powerPlot}, note how the proposed method produces a bus load that mirrors the uncontrolled load, yielding the flat load profile from Fig. \ref{fig:results:totalPower} which is especially prevalent from 7:12 to 14:24. The results show that the proposed method works well, outperforming both historical patterns at UTA as well and improves upon prior academic techniques.
\input{media/11_results/costComparison} 
\input{media/11_results/powerPlot}
\input{media/11_results/totalPower}
\subsection{Optimality Gap and Contention Trade-Off}
In the previous section, we compared performance of three methods where each method was solved optimally so that the optimality gap was small. In general, the most computationally demanding solution addressed bus-to-charger placement and can requre a very small gap to yield good solutions. 
\par This work also seeks to address how to compute a solution in a scalable manner and so this section reviews the relationship between computation time and the number of buses by considering a 7-charger scenario with runtime comparisons for 8, 9, and 10 buses. 
\par Fig. \ref{fig:results:scalabilityTimeVsGap} plots the computation time as a function of optimality for a 7-charger 8-bus scenario in blue, a 7-charger 9-bus scenario in red, and a 7-charger 10-bus scenario in green. In each scenario, note how there exists a gap after which computation time severly increases for small improvements in the optimality gap. Solving $P_5$ to an optimality gap after this point becomes computationally expensive and should be avoided in scalable solutions. 
\par Additionally, note how the untractable region for the 8-bus scenario begins at a smaller gap then that of the 9 or 10-bus scenarios. This demonstrates a relationship between contention and computation time as contention increases with the number of buses if the number of chargers is fixed. We can conclude therefore, that if the system is to scale, we must find a way to avoid computing solutions to small gaps where the number of computations becomes too large.
\input{media/11_results/scalabilityTimeVsGap}
\input{media/11_results/sessionComparison} 
\subsection{Contention: Sub-Optimal Schedules}
In the previous section we observed that the proposed method cannot scale with contention if the optimality gap enters the untractable region. This section considers an experiment to motivate the division into groups from $P_3$. The focus of this experimentn is to compare the the duration and charge rates of a small-gap and large-gap scenario. Solutions to $P_5$ are considered more optimal if session lengths are longer and require smaller charge rates because long charge sessions are logistically more tractable and small charge rates are easier to implement on charging hardware. 
\par Fig. \ref{fig:results:sessionComparison} displays the charge session durations as a function of charge rate for two solutions to an 18 bus 6 charger scenario. The first solution, shown in blue, was computed with a small optimality gap and the second, shown in red, was computed for a large optimality gap. Note how the charge sessions from the small-gap solution tend to have larger session durations and lower charge rates than the solution for the large-gap scenario, indicating the need for smaller gaps.
\par We further illustrate the difference in optimality by directly comparing the charge schedules for each scenario in Fig. \ref{fig:results:disoptimalRoutes} and Fig. \ref{fig:results:optimalRoutes}. In each figure, the color at the $i,j$ location represents the charge rate for bus $i$ at time $j$. Observe how the first sessions for buses 1 -- 4 and 6 -- 13 are assigned to a single charger in Fig. \ref{Fig:results:disoptimalRoutes} so that each charge session is compressed to accomodate the large number of buses. The remaining the remaining chargers appear to have one session at most which implies that charge sessions were poorly managed in the large-gap scenario. In comparison, the small-gap solution in Fig. \ref{fig:results:optimalRoutes} yields a more evenly distributed session load for each charger so that each session is lengthened, and contains smaller charge rates.
\par It is also interesting to note that the monthly costs of each solution may or may not be equivalent even though an small-gap solution is clearly superior. Therefore, a small gap is required to consistently achieve optimal session placement. We also know from Fig. \ref{fig:results:scalabilityTimeVsGap} that small optimality gaps may increase the number of computations so that the charger assignment problem becomes untractable for large numbers of buses, making it necessary to reduce the problem scope by dividing buses into groups. 
\input{media/11_results/disoptimalRoutes.tex}
\input{media/11_results/optimalRoutes.tex} 

\subsection{The Importance of Groups}
One contribution this work provides is a {\it scalable} way to compute cost-oriented charge schedules. We know from the previous section that the charger assignment problem will not scale for small optimality gaps. This section describes how the computational complexity of the charger assignment problem can be managed by separating the buses into groups so that the charger assignment problem can be solved for each group independently. 
\par In this section, we consider a 18 bus, 12 charger scenario with a 0.13\% gap in the charger assignment problem. Fig. \ref{fig:results:groupResults}, shows the respective runtimes for a one and two group scenario in $P_5$. Note how the runtime for the two group scenario is several orders of magnitude less then the runtime for the single group case which demonstrates how a small number of groups can manage the runtime for optimal charger assignment solutions.
\input{media/11_results/groupResults} 
\subsection{Effects of De-Fragmentation}
This paper also addresses the operational preference to consolidate charge sessions when possible, an operation we have called defragmentation. This section demonstrates the effectiveness of the defragmentation method given in $P_4$ and how consolidation affects the monthly cost. In section \ref{sec:defragmentation}, the threshold for defragmentation is given by the minimum allowable energy per charge session. In this section we compare two 40 bus 7 charger scenarios where the first contains results without defragmentation and the second consolidates charge sessions so that each session delivers at least 30 kWh. The results for each session are presented in Figures \ref{fig:results:noFragmentationChargeLimit} and \ref{fig:results:defragmentedChargeLimit} where the color of $i,j$ element of a figure represents the charge rate for bus $i$ during time $j$. Note how Fig. \ref{fig:results:noFragmentationChargeLimit} contains {\it many} small an inconsequential charge sessions and requires each bus to charge each time it enters the station. In comparison, Fig. \ref{fig:results:defragmentedChargeLimit} contains only a handful of charge sessions so that each bus only need charge 4 -- 5 times throughout the day.  
\par Furthermore, Fig. \ref{fig:results:defragmentationCostProTime}, which plots monthly cost as a function of the minimum charging threshold, demonstrates that despite the additional constraints associated with consolidation, the monthly cost remains consistent over a large window of thresholds. As the minimum allowable energy per session increases, the number of binary variables in the defragmentation problem increases, resulting in significant runtimes for the defragmentation problem as shown in Fig. \ref{fig:results:defragmentationTimeProTime}, which plots runtime as a function of the minimum charge threshold. However, because buses are divided into groups prior to defragmentation, the smaller groups decrease the computational complexity for defragmentation so that larger consolidation thresholds can be applied in a scalable manner. 
\input{media/11_results/noFragmentationChargeLimit} 
\input{media/11_results/defragmentedChargeLimit}
\input{media/11_results/defragmentationCostProTime}
\input{media/11_results/defragmentationTimeProTime}
\subsection{Scalability}
In this section, we consolidate what we have learned in the previous sections to demonstrate how the proposed framework can be used to compute a scalable and cost effective solution for large numbers of buses. This section focuses on a scenario with a minimum energy per session of 20 kWh, a large gap for the charger assignment solution, and a single group.
\par The results are given in Fig. \ref{fig:results:scalabilityRuntimes}, which plots the runtime as a function of the number of buses and shows how that runtime generally increases by one second per bus from 10 to 110 buses.  One would expect the runtime to increase at least on the order of $O(n^2)$ for a globally optimal solution because of the coupling between bus variables. The fact that the proposed method is tractable on the given range indicates a scalable solution. 
\par Generally, one would also expect such savings to come with significant increases to the monthly cost. The results in Fig. \ref{fig:results:scalabilityCosts} however demonstrate how the proposed solution yields a quasi-linear increase of approximately \$404.10 dollars per bus per month. 
\input{media/11_results/scalabilityRuntimes}
\input{media/11_results/scalabilityCosts}
	
	
